Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm_intro.tex
changed min to sup

When multiple arms are payment-eligible, the algorithm picks one arbitarily to incentivize.
When the algorithm decides to incentivize an arm $i$,
it offers ``whatever it takes,'' i.e., offers a payment of
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
The maximum for \AgV is taken over the support of \AgentDist;
recall that we assumed this support to be compact.
The payment \Pay{t}{i} may appear unnecessarily high.
Indeed, it suffices to
incentivize only a $1/\log(s)$ fraction of the agents,
and our bounds also hold for an alternate version of our algorithm that 
offers payment
$\Pay{t}{i} = \min \Set{c \geq 0}{%
\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
However, we focus on the higher payments for simplicity of presentation.

>>>>

When multiple arms are payment-eligible, the algorithm picks one arbitarily to incentivize.
When the algorithm decides to incentivize an arm $i$,
it offers ``whatever it takes,'' i.e., offers a payment of
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
The maximum for \AgV is taken over the support of \AgentDist;
recall that we assumed this support to be compact.
The payment \Pay{t}{i} may appear unnecessarily high.
Indeed, it suffices to
incentivize only a $1/\log(s)$ fraction of the agents,
and our bounds also hold for an alternate version of our algorithm that 
offers payment
$\Pay{t}{i} = \sup \Set{c \geq 0}{%
\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \leq 1/\log(s)}$.
(This definition ensures that \Pay{t}{i} is well-defined
and incentivizes at least a $1/\log(s)$ measure of agents,
even if $f$ has discrete points.)
However, we focus on the higher payments for simplicity of presentation.
